The Five Pillars of Translational Digital Medicine

### 2022-04-30 main.tex
discussion and edits from nel

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Sample {et~al.}} %use et al only if is more than 1 author
\def\Authors{Steve Harris\,$^{1,2*}$, Thomas Keen\,$^{1}$ Tim Bonnici\,$^{1,2}$ Watjana Lilaonitkul\,$^{1}$ and Nel Swanepoel\,$^{3}$}
% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.

\def\Address{$^{1}$Institute of Health Informatics, University College London, London, UK \\
$^{2}$Department of Critical Care, University College London Hospital, London, UK  \\
$^{3}$Centre for Advanced Research Computing, University College London, London, UK  }

@@

SH is supported by a Health Foundation Improvement Science Fellowship, and by funding from 
Biomedical Research Centre based at the University College Hospitals (UCLH) National Health Service (NHS) Foundation Trust and University College London (UCL). SH, TK, and NS are supported funds from the National Institute for Health Research (Artificial Intelligence, Digitally adapted, hyper-local real-time bed forecasting to manage flow for NHS wards, AI AWARD01786) and NHS-X. The views expressed in this publication are those of the author(s) and not necessarily those of the National Institute for Health Research, NHS-X or the Department of Health and Social Care. WL is supported by a

>>>>

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Sample {et~al.}} %use et al only if is more than 1 author
\def\Authors{Steve Harris\,$^{1,2*}$, Tim Bonnici\,$^{1,2}$ Thomas Keen\,$^{1}$ Watjana Lilaonitkul\,$^{1}$ Nel Swanepoel\,$^{3}$ Mark White\,$^{4}$}
% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.

\def\Address{$^{1}$Institute of Health Informatics, University College London, London, UK \\
$^{2}$Department of Critical Care, University College London Hospital, London, UK  \\
$^{3}$Centre for Advanced Research Computing, University College London, London, UK \\
$^{4}$Digital Healthcare, University College London Hospital, London, UK   }

@@

SH is supported by a Health Foundation Improvement Science Fellowship, and by funding from 
Biomedical Research Centre based at the University College Hospitals (UCLH) National Health Service (NHS) Foundation Trust and University College London (UCL). NS is supported by funding from Health Data Research UK. SH, TK, and NS are supported funds from the National Institute for Health Research (Artificial Intelligence, Digitally adapted, hyper-local real-time bed forecasting to manage flow for NHS wards, AI AWARD01786) and NHS-X. The views expressed in this publication are those of the author(s) and not necessarily those of the National Institute for Health Research, NHS-X or the Department of Health and Social Care. WL is supported by a UKRI Ernest Rutherford Fellowship.
